Comparing the Jacobi Method and LLL lattice reduction algorithms for cryptographic applications

### 2014-12-18 report/presentation.tex
Presentation state

\frame{\frametitle{Lattice}
\begin{columns}[]
 \begin{column}{0.3\textwidth}
\input{figlat/linearcodesballs}
 \end{column}
 \begin{column}{0.7\textwidth}
 	\begin{itemize}
 	\item Set $B=\{\vec{b}_1,..,\vec{b}_n\} \subset\R^m$, \\$\vec{b}_i$ are linearly independent
 	\item Full-rank lattices: $n = m$
 	\begin{block}{}
	Set of \alert{integer} linear combinations
 	$$\text{Lattice }\Ls = \sum_i \alert{\Z}\cdot \vec{b}_i $$
 	\end{block}
	\item $B$ is called a basis of $\Ls$, it is not unique
	\end{itemize}
 \end{column}
\end{columns}
}

\frame{
\frametitle{Short vectors}
\begin{columns}[]
  \begin{column}{0.3\textwidth}
\input{figlat/latminimum}
  \end{column}
  \begin{column}{0.7\textwidth}
  Norm of a vector $\vec{x}$ is given by $\|\vec{x}\| := \sqrt{\sum x^2_i}$
  \begin{block}{First lattice minimum}
 	\begin{itemize}
 	\item Length of a shortest vector of a $n$-dimensional lattice $\Ls$:
 	\begin{eqnarray*} 
 	\lambda_1(\Ls)% &= &\min\limits_{x,y\in \Ls, x\neq y} \|x-y\|\\
 	&:= &\min\limits_{x\in \Ls, x\neq 0} \|x\|
 		\end{eqnarray*} 	
 			\item Minimal distance between two lattice vectors
 				\end{itemize}
 				\end{block}
 \end{column}
\end{columns}
}

\frame{
\frametitle{Shortest vector problem }
\begin{columns}[]
  \begin{column}{0.3\textwidth}
    \input{figlat/latSVP}
  \end{column}
  \begin{column}{0.7\textwidth}
 	\begin{itemize}
 	\item Shortest vector problem ($SVP_2$) \\
 	Given $B$, find $v\in \Ls\backslash\{0\}$ of minimal length.\vspace{.3cm}
 	\pause 
 	\item Problem is hard for large dimensions and a skewed??????????? basis 
	\end{itemize}
 \end{column}
\end{columns}
}

@@

@@

>>>>

\frame{\frametitle{Lattice}
\begin{columns}[]
 \begin{column}{0.3\textwidth}
\input{figlat/linearcodesballs}
 \end{column}
 \begin{column}{0.7\textwidth}
 	\begin{itemize}
 	\item Set $B=\{\vec{b}_1,..,\vec{b}_n\} \subset\R^m$, \\$\vec{b}_i$ are linearly independent
 	\item Full-rank lattices: $n = m$
 	\begin{block}{}
	Set of \alert{integer} linear combinations
 	$$\text{Lattice }\Ls = \sum_i \alert{\Z}\cdot \vec{b}_i $$
 	\end{block}
	\item $B$ is called a basis of $\Ls$, it is not unique
	\item the volume of a full-rank lattice is given by $\text{vol}(\Ls) = |det(B)|$
	\end{itemize}
 \end{column}
\end{columns}
}

@@

\frame{
\frametitle{Gram Schmidt orthogonalisation - GSO}
\begin{itemize}
\item Basis $B = (\vec{b}_1, \ldots, \vec{b}_n)$
\item Compute GSO of $B$:\\
 $\vec{b}_1^* = \vec{b}_1$\\
 $\vec{b}_2^* = \vec{b}_2 - \frac{\langle b_2, b_1^*\rangle}{\|\vec{b}_1\|^2} \vec{b}_1$\\
  $\vec{b}_3^* = \vec{b}_3 - \frac{\langle b_3, b_1^*\rangle}{\|b_1\|^2} \vec{b}^*_1- \frac{\langle b_3, b_2^*\rangle}{\|b_2^*\|^2} \vec{b}_2^*$\\
  $\ldots$

  \vspace{.3cm}
%\item Obtain $\pi_i(b_i) = b_i^*$ as\\
\item In general 
 $$\vec{b}_i^* = \vec{b}_i - \sum_{j<i}  \mu_{ij}  \vec{b}_j^* \text{ where }\mu_{ij} := \frac {\langle b_i, b_j^*\rangle} { \|b_j^*\|^2 }$$
\end{itemize}
}

@@

\frame{
\frametitle{Jacobi after LLL}
\begin{block}{Example of LLL-reduced basis but not Jacobi-reduced}

\[
B = \begin{bmatrix}
  \vec{b_1} \\
  \vec{b_2} \\
  \vec{b_3}
 \end{bmatrix} = \begin{bmatrix}
  0 & 2 & 0 \\
  0 & 1 & 2 \\
  2 & 0 & 0
 \end{bmatrix}
\]
\end{block}
}
